\tit

### 2021-02-27 paper.tex
automata perspective

\begin{comment}
Lemma \AF{ν∘foldlδ} relates to some other powerful perspectives and principles as well:
\begin{itemize}

\item 
\emph{Automata theory}: {\AF{ν} \AF ∘ \AF{foldl} \AF{δ} \AB{P}} is the execution of a state machine.
Each state is a language, with \AB{P} being the initial state; \AF{δ} is the state transition function; and \AB{ν} is the set of accepting states\out{ \needcite{}}.
Lemma \AF{ν∘foldlδ} captures the correctness of this state machine as a recognizer for the language \AB{P}.

\item
\emph{Incremental computation}: {\AF{ν} \AF ∘ \AF{foldl} \AF{δ} \AB{P}} computes \AB{P} by transforming successive incremental modifications to the empty string (each in the form of {\AB{a} \AIC ∷\_} for a list element \AB{a}) into incremental modifications to the membership question for the related language {\AF{δ} \AB{P} \AB{a}}\out{ \needcite{}}.
Lemma \AF{ν∘foldlδ} again captures the correctness of this incremental implementation of \AB{P}.

\item 
\emph{Calculus}: \AB{δ} is differentiation; {\AF{ν} \AF ∘ \AF{foldl} \AF{δ} \AB{P}} is integration; and lemma \AF{ν∘foldlδ} is the second fundamental theorem of calculus, which says that a function can be recovered by integrating its derivative\out{ \needcite{}}.

\end{itemize}
\end{comment}

>>>>

In terms of automata theory, derived languages are states, with \AB{P} being the initial state and {\AF{𝒟} \AB{P} \AB{u}} the state reached from \AB{P} after consuming the string \AB{u}; \AF{δ} is the state transition function; and \AB{ν} is the set of accepting states\out{ \needcite{}}.
Lemmas \AF{ν∘𝒟} and \AF{𝒟foldl} capture the correctness of this state machine as a recognizer for the language \AB{P}.
